Individual Stellar Halos of Massive Galaxies Measured to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-09-17 draft/paper1_v14.tex
For referee report

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH
% Version 10; MNRAS format; Edited by AL and JG
% Version 11; MNRAS format; Edited by SH
% Version 12; MNRAS format; Edited by SH
% Version 13; MNRAS format; Edited by KB

@@

    Massive galaxies display extended light profiles that can reach several 
    hundreds of kilo parsecs. 
    These stellar halos provide a fossil record of galaxy assembly histories. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$ with $log M_{\star}/M_{\odot} > 11.4$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which enables us to individually 
    estimate surface mass density profiles to 100 kpc without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles.  
    When this extended light is not properly accounted for as a result of shallow imaging 
    or inadequate profile modeling, the derived stellar mass function can be 
    significantly underestimated at the highest masses.  
    Across our sample, the ellipticity of outer light profiles increases substantially 
    as we probe larger radii.  
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at late times from a series of merging events. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

@@

    % TODO: Move this to Paper II
    %To ensure a clean separation in \mhalo{}, here we only focus on the central 
    %galaxies of clusters with $\lambda > 30$. 
    %According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
    %$M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
    %We have checked that none of the results in this work depend on the choice of this 
    %$\lambda$ limit.

    %The median $\lambda$ of the clusters associated with the \rbcg{} sample is 
    %${\sim} 41$, corresponding to halo mass of 
    %$M_{\mathrm{halo}}{\sim} 2.2\times 10^{14}$ $h^{-1}$ $M_{\odot}$.
    %Only 44 centrals from the \rbcg{} sample live in clusters with $\lambda \geq 50$
    %($M_{\mathrm{halo}} {\sim} 3.0\times 10^{14}$ $h^{-1} M_{\odot}$). 
    %Our \rbcg{} sample therefore corresponds to galaxies in moderate mass halos.

    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
    clusters with $\lambda \geq 20$ and $P_{\mathrm{Cen}} \geq 0.7$, we find 164 
    matched galaxies at $0.3 \leq z \leq 0.5$.
    This sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    It is also worth pointing out that, due to the depth and resolution of SDSS 
    images, this \redm{} catalog is not complete down to $\lambda=20$ at 
    $0.3 < z < 0.5$. 
    At $z\geq0.33$, it starts to miss a small fraction of clusters with $\lambda < 30$, 
    but the main results of this work will not be affected by this.
    %% Saved as "dr1_redbcg_use_sed5b.fits"

>>>>

% Version 0; preprint format; Written by SH
% Version 1; emulateapj format; Edited by SH and AL
% Version 2; emulateapj format; Edited by SH and AL
% Version 3; emulateapj format; Edited AL
% Version 4; emulateapj format; Edited SH
% Version 5; MNRAS format; Edited SH
% Version 6; MNRAS format; Paper I edited by JG
% Version 7; MNRAS format; Edited by SH
% Version 10; MNRAS format; Edited by AL and JG
% Version 11; MNRAS format; Edited by SH
% Version 12; MNRAS format; Edited by SH
% Version 13; MNRAS format; Edited by KB
% Version 14; MNRAS format; Edited by SH, response to referee report

@@

    Massive galaxies display extended light profiles that can reach several 
    hundreds of kilo parsecs. 
    These stellar halos provide a fossil record of galaxy assembly histories. 
    Using data that is both wide (${\sim}100$ deg$^2$) and deep ($>28.5$ \sb{} in 
    $i$-band), we present a systematic study of the stellar halos of a sample of more 
    than $7000$ galaxies at $0.3 < z < 0.5$ with $\log M_{\star}/M_{\odot} > 11.4$. 
    Our study is based on high-quality (0.6\asec\ seeing) imaging data from the Hyper 
    Suprime-Cam (HSC) Subaru Strategic Program (SSP), which enables us to individually 
    estimate surface mass density profiles to 100 kpc without stacking. 
    As in previous work, we find that more massive galaxies exhibit more extended outer 
    profiles.  
    When this extended light is not properly accounted for as a result of shallow imaging 
    or inadequate profile modeling, the derived stellar mass function can be 
    significantly underestimated at the highest masses.  
    Across our sample, the ellipticity of outer light profiles increases substantially 
    as we probe larger radii.  
    We show for the first time that these ellipticity gradients steepen dramatically as 
    a function of galaxy mass, but we detect no mass-dependence in outer color gradients. 
    Our results support the two-phase formation scenario for massive galaxies in which 
    outer envelopes are built up at late times from a series of merging events. 
    We provide surface mass surface mass density profiles in a convenient tabulated format 
    to facilitate comparisons with predictions from numerical simulations of 
    galaxy formation.

@@

    After matching the \texttt{hscZ} sample with the central galaxies of \redm{} 
    clusters with $\lambda \geq 20$ and $P_{\mathrm{Cen}} \geq 0.7$, we find 164 
    matched galaxies at $0.3 \leq z \leq 0.5$.
    This sample of \textbf{central galaxies in more massive halos} will be referred to 
    as the \rbcg{} sample. 
    It is also worth pointing out that, due to the depth and resolution of SDSS 
    images, this \redm{} catalog is not complete down to $\lambda=20$ at 
    $0.3 < z < 0.5$. 
    At $z \geq 0.33$, it starts to miss a small fraction of clusters with $\lambda < 30$, 
    but the main results of this work will not be affected by this.
    %% Saved as "dr1_redbcg_use_sed5b.fits"
